A Two-Infall Star Formation History with Outflows and Radial Migration

### 2024-11-04 src/tex/ms.tex

@@

\citet{chiappini_chemical_1997} presented the first two-infall model of the MW disk. They adopted an inside-out prescription for the formation of the thin disk, with the timescale of the second infall varying with radius. Their model parameters were constrained by the observed

@@

\begin{table}
    \centering
    \caption{Yields.}
    \label{tab:yields}
    \include{output/yields.tex}
\end{table}

@@

>>>>

\subsection{Summary of Two-Infall Papers}

@@

\citet{chiappini_chemical_1997} presented the first two-infall model of the MW disk. They adopted an inside-out prescription for the formation of the thin disk, with the timescale of the second infall increasing linearly with radius. They assume the formation timescale of the thick disk is 1 Gyr, and the time of the second infall is 2 Gyr. They also assume a lower threshold on the gas density required for star formation, which produces a star formation hiatus at the end of the thick disk phase. They also noted the ``loop'' that appears in the \aFe--[Fe/H] relation during the thin disk phase.

\citet{palla_chemical_2020} explored radial gas flows, variable star formation efficiency of the thin disk, and the onset time of the second infall (but not the infall timescales). They find that inside-out formation (i.e., longer infall timescales in the outer disk) is not sufficient to reproduce observed abundance gradients, and that radial gas flows, possibly in combination with a radially-varying star formation law, are key. Pre-enriched infall in the inner disk ($R<8$ kpc) at the level of -0.5 dex also improves agreement with data.

@@

The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain. This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}. We adopt the yields of \citet{weinberg_scale_2023}, who use a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau to infer population-averaged yields. The only difference here is that we assume that $20\%$ of Si in the Sun is produced by SNe Ia, which reduces the Si plateau to [Si/Fe]$_{\rm cc}=0.35$ and results in a non-zero value for $y_{\rm SI}^{\rm cc}$, unlike in \citet{weinberg_scale_2023}. Our yields are presented in Table \ref{tab:yields}.

\begin{table}
    \centering
    \caption{Nucleosynthetic yields.}
    \label{tab:yields}
    \include{output/yields.tex}
\end{table}

\subsection{Outflows}
\label{sec:outflows}

@@

We adopt the wide plateau DTD of \citet{dubay_galactic_2024} as our fiducial DTD.

\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}^{\rm plat}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}
